\Large Carryover effects in free recall reveal how past experiences influence memories of future experiences

### 2023-01-16 paper/main.tex
added keywords, backing up progress on discussion

\title{Carryover effects in free recall reveal how past experiences influence
memories of future experiences}

@@

\begin{abstract} We perceive, interpet, and remember ongoing experiences
through the lens of our prior experiences. Inferring that we are in one type of
situation versus another can lead us to interpret the same physical experience
differently. In turn, this can affect how we focus our attention, form
expectations about what will happen next, remember what is happening now, draw on
our prior related experiences, and so on. To study these phenomena, we asked
participants to perform simple word list learning tasks. Across different
experimental conditions, we held the set of to-be-learned words constant, but
we manipulated the orders in which the words were studied. We found that these
order manipulations affected not only how the participants recalled the ordered
lists, but also how they recalled later randomly ordered lists. Our work shows
how structure in our ongoing experiences can exert influence on how we remember
unrelated subsequent experiences. \end{abstract}

>>>>

\title{\Large Carryover effects in free recall reveal how past experiences influence
memories of future experiences}

@@

\begin{abstract} \footnotesize{We perceive, interpet, and remember ongoing experiences
through the lens of our prior experiences. Inferring that we are in one type of
situation versus another can lead us to interpret the same physical experience
differently. In turn, this can affect how we focus our attention, form
expectations about what will happen next, remember what is happening now, draw on
our prior related experiences, and so on. To study these phenomena, we asked
participants to perform simple word list learning tasks. Across different
experimental conditions, we held the set of to-be-learned words constant, but
we manipulated the orders in which the words were studied. We found that these
order manipulations affected not only how the participants recalled the ordered
lists, but also how they recalled later randomly ordered lists. Our work shows
how structure in our ongoing experiences can exert influence on how we remember
unrelated subsequent experiences.

\textbf{Keywords: episodic memory, free recall, incidental features, implicit priming, temporal order}}

\end{abstract}
